### 2025-12-12 README.Rmd

If you're interested in learning more about randomization-based statistical inference generally, including applied examples of this package, we recommend checking out [Statistical Inference Via Data Science: A ModernDive Into R and the Tidyverse](https://moderndive.com/) and [Introduction to Modern Statistics](https://openintro-ims.netlify.app/).

>>>>

If you're interested in learning more about randomization-based statistical inference generally, including applied examples of this package, we recommend checking out [Statistical Inference Via Data Science: A ModernDive Into R and the Tidyverse](https://moderndive.com/v2/) and [Introduction to Modern Statistics](https://openintro-ims.netlify.app/).

### 2025-12-12 man-roxygen/seeds.Rmd

gss %>%
  specify(age ~ college) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 5, type = "permute") %>%
  calculate("diff in means", order = c("degree", "no degree"))
```

>>>>

gss |>
  specify(age ~ college) |>
  hypothesize(null = "independence") |>
  generate(reps = 5, type = "permute") |>
  calculate("diff in means", order = c("degree", "no degree"))
```
